Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-07-11 rmd/manuscript.Rmd
edit

@@

No primary data were used or produced in this research. R functions for simulations are provided as the R package mcbrnet version 1.3.1 (available at <https://github.com/aterui/mcbrnet>). Codes for simulations, statistical analysis, figures, and tables are available at <https://github.com/aterui/public-proj_fcl-river-theory>.

@@

knitr::kable(df_value %>%
               dplyr::select(-"One-patch") %>%
               rename(Value = "Main"),
             escape = FALSE,
             booktabs = TRUE,
             caption = "Parameter values used in the main simulation")
```

>>>>

Track: Freshwater Ecology

@@

No primary data were used or produced in this research. R functions for simulations are provided as the R package mcbrnet version 1.3.1 (available at <https://github.com/aterui/mcbrnet>) [@teruiMcbrnetMetacommunitySimulation2023]. Codes for simulations, statistical analysis, figures, and tables are available at <https://github.com/aterui/public-proj_fcl-river-theory> [@pomeranzCodeEcosystemSize2023].

@@

knitr::kable(df_value %>%
               dplyr::select(-"One-patch") %>%
               rename(Value = "Main"),
             escape = FALSE,
             booktabs = TRUE,
             caption = "Table 1: Parameter values used in the main simulation")
```
